%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Niharika}{Sharma}{
 \href{mailto:niharikasharma463@gmail.com}{niharikasharma463@gmail.com} | +91 9304330174 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{R.V.S. College of }
\subsection{Engineering}
\subsection{And technology}
\descript{Bachelor's Degree in Computer Science}
\location{2017-21 | Jamshedpur,JH}
\location{GPA : 8.4 / 10}
\sectionsep

\subsection{Gossner College}
\descript{Intermediate in Science}
\location{2015-17 | Ranchi,JH}
\location{GPA: 6 / 10}
\sectionsep

\subsection{D.A.V. Public School}
\descript{Matriculation}
\location{2014- 15 | Dhanbad,JH}
\location{GPA: 9.6 / 10}
\sectionsep

% \subsection{La Martiniere for Boys}
% \location{Grad. May 2011|  Kolkata, India}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/Niharika100}{\bf Niharika100} \\
LinkedIn:// \href{https://www.linkedin.com/in/niharikasharma196747151/}{\bf niharikasharma196747151} \\
HackerRank:// \href{https://www.hackerrank.com/niharikasharma42}{\bf niharikasharma42} \\
GeeksForGeeks:// \href{https://auth.geeksforgeeks.org/user/arunimasharma1/profile}{\bf arunimasharma1} \\
LeetCode:// \href{https://leetcode.com/niharikasharma463/}{\bf niharikasharma463}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\section{Coursework}
\subsection{UNDERGRADUATE}
Data Structures and Algorithms\\
Database Management Systems\\
Operating Systems\\
File Structures\\
Computer Networks\\
Object Oriented Programming\\
Unix Tools and Scripting\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Over 10,000 lines:}
\textbullet{} VanillaJS
\textbullet{} Express
\textbullet{} NodeJS 
\textbullet{} React Native 
\textbullet{} REST API
\textbullet{} Sockets \\
\location{Database} 
\textbullet{} NoSQL(MongoDB)
\textbullet{} MySQL \\
\location{Academic Experience} 
\textbullet{} C++ 
\textbullet{} Python 
\textbullet{} HTML / CSS 
\textbullet{} Bootstrap \\
\location{Familiar} 
\textbullet{} GitHub 
\textbullet{} Bitbucket
\textbullet{} Redis(cache)
\textbullet{} Nginx
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{2gethr}
\descript{| Full-stack Engineer }
\location{Jan 2021 - Present | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Working on the frontend and backend of a social network like application with \textbf{sockets} from scratch providing \textbf{multi-tenanted access} with Role Based Access Control.
\item Working on \textbf{co-working applications} (for clients and and internal members)
\end{tightemize}

\sectionsep

\runsubsection{Pathfold}
\descript{| Internship }
\location{May 2020 – Sep 2020 | Web Development}
\begin{tightemize}
\item Supported staff activities to assist \textbf{web page launches}.
\item Crafted \textbf{mobile-friendly websites} and transitioned the legacy site to a mobile-friendly platform.
\end{tightemize}

\location{April 2020 – May 2020 | Data Analysis}
\begin{tightemize}
\item Achieved \textbf{Data Analysis Concepts using Python} within 1 month of Training.
\item Done Hands-on practice on Compound Data and delivered the output within the given time period.
\item Reviewed and updated \textbf{account information in company computer system}.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
{\href{https://github.com/Niharika100/Niharika100-bookRoom_backend}{\bf{\runsubsection{Meeting Room Bookings}}}}
\descript{| 2021}
\location{NodeJS, REST, MongoDB}
\descript {A project used to manage the room bookings} 
\begin{tightemize}
\item Built this application to help users \textbf{create new rooms} and and \textbf{book the seats} in a particular room.
\item It helps to \textbf{avoid the conflict between multiple users} while booking same seats.
\end{tightemize}

\sectionsep

{\href{https://niharika100.github.io/nearEarthObjectStats/}{\bf\runsubsection{{Asteroid NEO Stats}}}}
\descript{| 2020}
\location{Bootstrap, JavaScript, NodeJS, Heroku}
\descript {Shows the stats of the objects passing the Earth within 7 days.}
\begin{tightemize}
\item Built this web page to help users \textbf{analyse the number of asteroids passing the Earth }with the fastest and the nearest Asteroid among them.
\item The main aim was \textbf{to avoid the complex API study of NASA}. 
\item In this web page, one can easily input the range of date within 7 days and check the Asteroids count.
\end{tightemize}
\sectionsep

{\href{https://github.com/Niharika100/WebChatApp}{\bf{\runsubsection{Single page Web Chat App}}}}
\descript{| 2020}
\location{JavaScript, NodeJS}
\descript{A real-time web chat app}
\begin{tightemize}
\item Created this mini app for fun to have temporary \textbf{group chat within neighbours.}
\item This project \textbf{solved a problem of interaction} while maintaining social distance.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
\begin{tabular}{rll}
2021	     & GATE Qualifier  & \bf{\href{https://drive.google.com/file/d/15GE8USUrYsOLWMyxbJCKXGUEODwfVKVF/view?usp=sharing}{Score Card}}\\
2020     & Coding Challenge Scaler Academy &  \bf{\href{https://drive.google.com/file/d/1FvnQb3Byb9vj0uEbBudwzwYHRNe2MFp1/view}{Certificate}} \\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
